Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Names are hard
Proofread

With the widespread use of the tablet and increasing availability of the Internet, several applications have been developed that are similar to {\em Kimbee}. Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}. The researchers created an application for children to speak words and receive feedback on whether the word they said matches what was on the screen. The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly. Because of this, the amount of time it would take a new student to get started is significant. Their application currently only supports the Spanish language, which would not be of much help to English speaking students. Our project's scope is almost much narrower. Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.

@@

We will now introduce our implementation and solution to the problem posed for children's speech therapy. Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}. Mr. Kreider has over 25 years of experience working with children to overcome their speech disorders. Mr. Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time. As these were the two most important features Mr. Kreider discussed, we designed Kimbee around them as core features.

@@

The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}. Children simply tap the screen to make their character, a bee, move along the y-axis of the screen. Collecting honey causes their score to increase and colliding with an enemy bee causes the game to end. Interleaved with the enemy bees and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed. This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.

@@

As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children. We wanted to have an application that children would see less as homework, and more of a game. This was the underlying motivation for making {\em Kimbee} a game. In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}. We were able to create this using the honey collected as a currency. We also added the dynamic scoring of the honey, with the collection of the pots and completion of the challenges.

Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}. For example, Mr. Kreider rewards children with small toys after they do well on a set of phrases. A reward system could be implemented where the currency is the honey from {\em Kimbee}. This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time. As this was only a quarter long project, this is left as future work.\label{sec:currency}

@@

\subsubsection{Phaser Game Implementation}
The {\em Phaser Game Implementation} of the {\em Game} encompasses the view and control of the application: The main menu, the game play, and rendering. This is what the children interact with to practice speech. The game is implemented with the Phaser Game Framework. Which represents screens of the game into states. States are linked together in meaningful ways. For example, the Main Menu State links to the Option Menu State via a Phaser Framework Button. It also provides image animation, tweening, and collision support. To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.

@@

\subsubsection{Data Models}
The server has three data models: recordings, children, and therapists. Recordings are the microphone encodings and recognition data from the {\em Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child, and their token obtained from their {\em Game} instance. Future recordings are then relayed to the therapist from this particular {\em Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

@@

Upon the completion of {\em Kimbee}, we met with Mr. Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}. His reaction was very positive. He found no real flaws with the application and expressed that it would be very useful for children to work with. He wants us to continue consulting and working with him in the future as he thought that {\em Kimbee} was very promising. He did have suggestions for the future that are listed below under section \ref{sec:future_work}. Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.

@@

We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}. We would also like to thank Bruce Hemingway and the TA for helping us throughout the project with guidance and feedback.

>>>>

With the widespread use of the tablet and increasing availability of the Internet, several applications have been developed that are similar to {\em Kimbee}. Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}. The researchers created an application for children to speak words and receive feedback on whether the word they said matches the correct pronunciation of what was on the screen. The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly. Because of this, the amount of time it would take a new student to get started is significant. Their application currently only supports the Spanish language, which would not be of much help to English speaking students. Our project's scope is almost much narrower. Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.

@@

We will now introduce our implementation and solution to the problem posed for children's speech therapy. Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}. Kreider has over 25 years of experience working with children to overcome their speech disorders. Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time. As these were the two most important features Kreider discussed, we designed Kimbee around them as core features.

@@

The game has a simple interface that is easy for a child to navigate, see Figure \ref{fig:user}. Children simply tap the screen to make their character, a bee, move along the y-axis of the screen. Collecting honey causes their score to increase and colliding with an enemy wasp causes the game to end. Interleaved with the enemy wasps and honey pots is a special honey pot that will grant a significant amount of honey if a challenge is completed. This challenge consists of having the child speak into the microphone of his or her device and say a designated word or phrase that appears on the screen.

@@

As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children. We wanted to have an application that children would see less as homework and more of a game. This was the underlying motivation for making {\em Kimbee} a game. In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}. We were able to create this using the honey collected as a currency. We also added the dynamic scoring of the honey, with the collection of the pots and completion of the challenges.

Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}. For example, Kreider rewards children with small toys after they do well on a set of phrases. A reward system could be implemented where the currency is the honey from {\em Kimbee}. This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time. As this was only a quarter long project, this is left as future work.\label{sec:currency}

@@

\subsubsection{Phaser Game Implementation}
The {\em Phaser Game Implementation} of the {\em Game} encompasses the view and control of the application: The main menu, the game play, and rendering. This is what the children interact with to practice speech. The game is implemented with the Phaser Game Framework  which represents screens of the game into states. States are linked together in meaningful ways. For example, the Main Menu State links to the Option Menu State via a Phaser Framework Button. It also provides image animation, tweening, and collision support. To create our microphone button, we extend the Phaser Framework Button and implement connections to the speech processing component while preserving button functionality through inheritance.

@@

\subsubsection{Data Models}
The server has three data models: recordings, children, and therapists. Recordings are the microphone encodings and recognition data from the {\em Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child and their token obtained from their {\em Game} instance. Future recordings are then relayed to the therapist from this particular {\em Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

@@

Upon the completion of {\em Kimbee}, we met with Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}. His reaction was very positive. He found no real flaws with the application and expressed that it would be very useful for children to work with. He wants us to continue consulting and working with him in the future as he thought that {\em Kimbee} was very promising. He did have suggestions for the future that are listed below under section \ref{sec:future_work}. Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.

@@

We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}. We would also like to thank Bruce Hemingway and Hanchuan Li for helping us throughout the project with guidance and feedback.
